\begin{comment}
\begin{frame}
  \frametitle{Precepts of this work}

  \begin{itemize}
  	\item \textbf{Visualization}: often crucial for scientific discovery and should be fundamental in statistical
	analysis.
	\epigraph{If I can't picture it, I can't understand it.}{Albert Einstein}
%	\epigraph{Science is like sex: sometimes something useful comes out,
%      but that is not the reason we are doing it}{Richard Feynman}
%    \epigraph{You can see a lot, just by looking}{Yogi Berra}
	\epigraph{In certain problems it was necessary to  
	develop the \alert{picture} as the method before the mathematics 
	could be really done}{Richard Feynman}


	\item \textbf{Theory into Practice}: 
	\epigraph{The practical power of a statistical test is the product
	of its' statistical power and the probability of use.}
	{J. W. Tukey, 1959\nocite{Tukey:59}}
	
	\item \textbf{Computation and Implementation}: 
	 \begin{itemize*}
	  \item Modern statistical methods are often computationally intensive (e.g., bootstrap, MCMC, asymptotics)
	  \item A general and correct implementation allows these to be tested  \alert{studied as statistical
	  objects} and \alert{find gaps} in theory or implementation.
	\end{itemize*}
  \end{itemize}
\end{frame}
\end{comment}

\begin{frame}
  \frametitle{Precepts of this work}

  \begin{block}<1->{\textbf{Visualization}} Should be fundamental in statistical theory \&
	practice.
	\epigraph{If I can't picture it, I can't understand it.}{Albert Einstein}
%	\epigraph{Science is like sex: sometimes something useful comes out,
%      but that is not the reason we are doing it}{Richard Feynman}
%    \epigraph{You can see a lot, just by looking}{Yogi Berra}
	\epigraph{In certain problems it was necessary to  
	develop the \alert{picture as the method} before the mathematics 
	could be really done}{Richard Feynman}
	\end{block}

	\begin{block}<2->{\textbf{Theory into Practice}}
	\epigraph{The \alert{practical power} of a statistical test is the product
	of its' statistical power and the probability of use.}
	{J. W. Tukey, 1959\nocite{Tukey:59}}
	\end{block}

	
	\begin{block}<3->{ \textbf{Computation and Implementation}}
	 \begin{itemize*}
	  \item Modern statistical methods are often 
	  mathematically complex and 
	  computationally intensive (e.g., bootstrap, MCMC, asymptotics)
	  \item A general implementation allows these to be tested  \alert{studied as statistical
	  objects} and \alert{find flaws} in theory or implementation.
	\end{itemize*}
  \end{block}

\end{frame}
